Quantifying and Modeling Global Water Accessibility including Water Typology

### 2021-01-19 docs/manuscript/manuscript.tex
{jagals2006does} highlights ... increased literature review.

@@

\citet{cassivi2021evaluating} focuses a case study in Southern Malawi, where data collected in March and April of 2019 at the conclusion of the rainy season. The sample was consisted of 375 households without access to water on their premises.   The article highlighted using Euclidean Distance measurement is more reliable than the self-reported time. Also queuing time measurement can be hard to be measured because of their ambiguity. Her Research gives greater insight into how do we define water accessibility and how increase of water accessibility can impact people's lives beneficially. 
% citep (for citations fully enclosed in parentheses)
% cite (for citations without any parentheses)
% citet (for citations where the year only is in parentheses)
%%\textit{Discuss the who/what/when/where? (You already have this... just need to reorganize or improve structure)}
%Another example is \citet{fuller2016tracking}.
%\citet{rawas2020comparing} highlights the need for different approaches of intermittent water supplies (IWS) to monitor piped water supply perpetually in Peru.
%\citet{cassivi2018access} discuss time access...
%\hl{Perhaps insert a table summarizing the various dimensions of water accessibility that have been studied}
%Other examples: \citep{amit2019measuring,ho2014challenge}
\subsection*{Gaps and areas for improvement}
We are interested in analyzing the impact of transportation modes (usage/ownership) on water accessibility. We also desire to see an implementation of this statistical research piloted in one of the countries to see if the water accessibility variables predictors can improve the water accessibility for its country.

>>>>

\citet{jagals2006does} highlights in his case study in rural area in South Africa discovered providing small communities, using untreated river water as their water source, with good quality water with a piped distribution system and increase of accessibility by installing communal taps did not fall within parameters of safe water. Their research gives a potential understanding even making the drinking water accessible might not improve the quality of the water itself.

@@

\citet{cassivi2021evaluating} focuses a case study in Southern Malawi, where data collected in March and April of 2019 at the conclusion of the rainy season. The sample was consisted of 375 households without access to water on their premises.   The article highlighted using Euclidean Distance measurement is more reliable than the self-reported time. Also queuing time measurement can be hard to be measured because of their ambiguity. Her Research gives greater insight into how do we define water accessibility and how increase of water accessibility can impact people's lives beneficially.

% citep (for citations fully enclosed in parentheses)
% cite (for citations without any parentheses)
% citet (for citations where the year only is in parentheses)
%%\textit{Discuss the who/what/when/where? (You already have this... just need to reorganize or improve structure)}
%Another example is \citet{fuller2016tracking}.
%\citet{rawas2020comparing} highlights the need for different approaches of intermittent water supplies (IWS) to monitor piped water supply perpetually in Peru.
%\citet{cassivi2018access} discuss time access...
%\hl{Perhaps insert a table summarizing the various dimensions of water accessibility that have been studied}
%Other examples: \citep{amit2019measuring,ho2014challenge}
\subsection*{Gaps and areas for improvement}
We are interested in analyzing the impact of transportation modes (usage/ownership) on water accessibility. We also desire to see an implementation of this statistical research piloted in one of the countries to see if the water accessibility variables predictors can improve the water accessibility for its country.
